Citation Analysis of Computer Science Publications

### 2019-12-10 Scientometrics/comp.tex
rearranged figures

\title{Citation Analysis of Computer Science Publications}
%\thanks{Grants or other notes
%about the article that should go on the front page should be
%placed here. General acknowledgments should be placed at the end of the article.}

\subtitle{Relationship To Other Fields}

%\titlerunning{Short form of title}        % if too long for running head

@@

In this study, we sought to extend the work of Salton and Bergmark to reflect a more current reality while also considering connections between computer science and other fields. As a source of computer science literature, we used DBLP, a reference bibliography for computer science~\cite{dblp_ref}. The DBLP bibliography covers publications from computer science and includes publications from hybrid fields, where they are considered pertinent to computer science research. The underlying assumption we made is that records in DBLP are greatly enriched for computer science even while recognizing that coverage may be incomplete and possibly biased. Cross-matching DBLP publications to records in the Scopus, abstract and citation database of peer-reviewed literature, enabled us to harvest the richer links in Scopus as well as extract links to publications from other disciplines. This cross-matching also allows the use of both journal and article based classifications when clustering documents. Using both direct citations and co-citations as the basis for clustering, we used DBLP articles from journals and conference proceedings for the period 1996-2015. We reconciled these clusters with the All Science Journal Classification (ASJC) developed and maintained by Scopus through a combination of automated and manual procedures. We describe below the high-level interactions of computer science within the Physical Sciences as well as with the Social Sciences and Life Sciences. [What did we find? Some kind of preview sentence!].

@@

For the purpose of this study, our working definition of the computer science literature was all publications in the DBLP bibliography published in the years 1996-2015, that had (i) a digital object identifier (DOI), and (ii) could also be matched to article identifiers in the Scopus bibliography. The process of selection and matching resulted in a dataset of 2,685,356 publications (Materials and Methods).

@@

@@

\begin{figure}[ht]
\centering
% Use the relevant command to insert your figure file.
% For example, with the graphicx package use
 \includegraphics[scale=0.5]{cocit_venn2.pdf}
% figure caption is below the figure
\caption{High-level disciplinary composition of publications in $\sim$2,000 clusters generated by variable-level clustering  of co-citation data.
%Variable Level Clustering. 
84,591 nodes from were matched to the 4 subject areas, 
27 major subject areas, and 334 minor subject areas in the Scopus ASJC classification. Since 82.5\% of these nodes were assigned more to than one minor subject category, 
we assigned fractional counts for the four subject areas that summed to 1 for each article. The figure shows a four way Venn Diagram~\cite{chen_venn_2011} illustrating the 
relative frequencies of publications from the Physical Sciences, Social Sciences, Life Sciences, and Health Sciences.}
\label{fig:cocitr_venn2}       % Give a unique label
\end{figure}

\emph{need to cite Granovetter somewhere for definition of strong and weak ties that Small refers to}

>>>>

\title{Citation Analysis of Computer Science Publications}
%\thanks{Grants or other notes
%about the article that should go on the front page should be
%placed here. General acknowledgments should be placed at the end of the article.}
\subtitle{Relationship To Other Fields}
%\titlerunning{Short form of title}        % if too long for running head

@@

In this study, we sought to extend the work of Salton and Bergmark to describe current trends while considering connections between computer science and other fields. As a source of computer science literature, we used DBLP, a reference bibliography for computer science~\cite{dblp_ref}. The DBLP bibliography covers publications from computer science and includes publications from hybrid fields, where they are considered pertinent to computer science research. The underlying assumption we made is that records in DBLP are greatly enriched for computer science even while recognizing that coverage may be incomplete and possibly biased. Cross-matching DBLP publications to records in the Scopus, abstract and citation database of peer-reviewed literature, enabled us to harvest the richer links in Scopus as well as extract links to publications from other disciplines. This cross-matching also allows the use of both journal and article based classifications when clustering documents. Using both direct citations and co-citations as the basis for clustering, we used DBLP articles from journals and conference proceedings for the period 1996-2015. We reconciled these clusters with the All Science Journal Classification (ASJC) developed and maintained by Scopus through a combination of automated and manual procedures. We describe below the high-level interactions of computer science within the Physical Sciences as well as with the Social Sciences and Life Sciences. [What did we find? Some kind of preview sentence!].

@@

For the purpose of this study, our working definition of the computer science literature was all publications in the DBLP bibliography published in the years 1996-2015, that had (i) a digital object identifier (DOI), and (ii) could also be matched to article identifiers in the Scopus bibliography. The process of selection and matching resulted in a dataset of 2,685,356 publications (Materials and Methods). Of these roughly 2.8 million publications, approximately 2.07 million were classified as COMP under subject area and 2.07 million similarly were assigned ASJC codes corresponding to the major subject area, Computer Science with the balance of 610,000 publications non-exclusively shared between 26 different major subject areas ranging from Engineering (330,048) to Dentistry (1). Thus, the sets of computer science publications in DBLP and Scopus are partially overlapping rather than DBLP being a perfect subset of Scopus. [the point being that we should justify our use of both journal and article level classifications].

@@

\emph{need to cite Granovetter somewhere for definition of strong and weak ties that Small refers to}
\clearpage

%%%%%%%%%
\section{Figures}
%%%%%%%%%

\newpage

\newpage

@@

\newpage

\newpage

\begin{figure}[ht]
% Use the relevant command to insert your figure file.
% For example, with the graphicx package use
  \includegraphics[scale=0.45]{scopus_dblp_heatmap3.pdf}
% figure caption is below the figure
\caption{Heat map for the clustering obtained by direct citation. The  y-axis (rows) correspond to topics, defined by Scopus characterizations, and the
x-axis (columns) represent the 20 different clusters.  
Each cluster is characterized by topics that label at least 10\% of the publications in the cluster.
 }
\label{fig:heatmap}       % Give a unique label
\end{figure}

\newpage
\begin{figure}[ht]
\centering
% Use the relevant command to insert your figure file.
% For example, with the graphicx package use
 \includegraphics[scale=0.5]{cocit_venn2.pdf}
% figure caption is below the figure
\caption{High-level disciplinary composition of publications in $\sim$2,000 clusters generated by variable-level clustering  of co-citation data.
%Variable Level Clustering. 
84,591 nodes from were matched to the 4 subject areas, 
27 major subject areas, and 334 minor subject areas in the Scopus ASJC classification. Since 82.5\% of these nodes were assigned more to than one minor subject category, 
we assigned fractional counts for the four subject areas that summed to 1 for each article. The figure shows a four way Venn Diagram~\cite{chen_venn_2011} illustrating the 
relative frequencies of publications from the Physical Sciences, Social Sciences, Life Sciences, and Health Sciences.}
\label{fig:cocitr_venn2}       % Give a unique label
\end{figure}

\newpage
